\documentclass[final,1p,times]{elsarticle}

\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multicol}

% correct bad hyphenation here
\hyphenation{}

\journal{Journal of Transportation Research Part C: Emerging Technologies}

\begin{document}

\begin{frontmatter}

\title{Indic@: a Cloud-based system for the simulation and testing of the dynamic
pantograph–catenary interaction
\tnoteref{funding}}

\tnotetext[funding]{Research partially supported by project.}

\author[albacete]{Jose A. Mateo\corref{corresponding_author}}
\cortext[corresponding_author]{The corresponding author.}
\ead{JoseAntonio.Mateo@uclm.es}

\author[albacete]{Enrique Arias}
\ead{Enrique.Arias@uclm.es@uclm.es}

\author[albacete]{Tomas Rojo}
\ead{Tomas.Rojo@uclm.es}

\author[albacete]{Fernando Cuartero}
\ead{Fernando.Cuartero@uclm.es}

\address[albacete]{Universidad de Castilla-La Mancha, Albacete, Spain, 02071.}

\begin{abstract}
In this paper, we present a Cloud-based system for simulating and 
testing the dynamic pantograph-catenary interaction.
This high-throughput system called Indic@ represents a disruptive movement in the way 
the catenary-pantograph interaction software is
delivered to the final user (engineering companies). From now, we move 
from desktop applications to Software as a Service (SaaS), 
where users have to forget initial setup costs, paying only 
for the use they consume. Moreover, we have implemented a web platform to
automatize the creation of test scenarios just providing the initial and final
value of the parameter one want to study. In addition to this, these test are run in
a private cloud deployed using the framework OpenNebula and KVM, where the deployment of the
virtual machines and the maintenance of the computing infrastructure 
is completely transparent to the final user. 

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
 Catenary-pantograph interaction \sep Cloud Computing \sep OpenNebula \sep Simulation \sep Software as a Service (SaaS) \sep High-throughput
\end{keyword}

\end{frontmatter}

\section{Introduction}\label{sec:introduction}
\input{Intro}

\section{Background}\label{sec:background}
\input{Background}
\section{Conclusions and Future Work}\label{sec:conclusions}
\input{Conclusions}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

\bibliographystyle{elsarticle-num}
\bibliography{bibliografia}

\end{document}
\endinput
